\documentclass [12pt, oneside] {book}

\usepackage{amssymb}
\renewcommand{\baselinestretch}{1.5}
\usepackage[utf8]{inputenc}
\usepackage{geometry}
\geometry{a4paper, portrait, margin=2.5cm}
\usepackage[round]{natbib}
\usepackage{graphicx} %package to manage images
\usepackage{dirtytalk}
\graphicspath{ {./images/} }
%\usepackage[rightcaption]{sidecap}
\usepackage[font=scriptsize, labelfont=bf]{caption}
\usepackage{wrapfig}
\usepackage{hyperref}
\usepackage[acronym, toc]{glossaries}
\usepackage{acronym} 
\usepackage[nottoc]{tocbibind}
\makeglossaries


\begin{document}
\input{titlepage.tex}
\pagenumbering{Roman}
\addcontentsline{toc}{section}{Acknowledgement}
\section*{Acknowledgement}
bla bla bla bla
\newpage
\section*{Abstract}
Since 1948, the Palestinian refugees are not allowed to go back to Palestine. The existence of the Israeli state prevented the Palestinian refugees to get back to their homes. Their houses and villages were depopulated and demolished. Traveling to Palestine could be intimidating for some people due to the perception that the western media have shown about the country. Palestinian refugees need to have access to see Palestine. Anybody who wants to visit the country, but has political situation concerns, must experience or see what to expect of a visit to Palestine. Action research was the concept of developing Glimpses from Palestine \acrlong{vr} application. The application development was based on the insights that were collected from interviews. The rebuilding of one of the demolished villages in \acrlong{vr} has given the application a historical and political aspect. The results show a strong connection between the second and third generations of Palestinians and Palestine. The transition of stories from grandparents to grandchildren in the diaspora and their effect on maintaining a strong relationship with the country. Also, the results showed the effect that Glimpses from Palestine has on people to preserve the value of their country and villages. This research explores the \acrlong{vr} as a new approach for documenting and displaying the historical events and facts of a country as Palestine, that the history and the demography of the country were changed due to political conflict. 
\addcontentsline{toc}{section}{Abstract}
\tableofcontents
\listoffigures
\input{Bibliocosas/glossary.tex}

\printglossary[type=\acronymtype, title=Abbreviations, nonumberlist]


\chapter{Introduction}
\pagenumbering{arabic}
\input{chapters/Introduction.tex}
\chapter{State of the Art}
\input{chapters/StateoftheArt.tex}
\chapter{Background}
\input{chapters/Background.tex}
\chapter{Methodology}
\input{chapters/Methodology.tex}
\chapter{Application Development}
\input{chapters/Application.tex}
\chapter{Results}
\input{chapters/Results.tex}
\chapter{Discussion}
\input{chapters/Discussion.tex}
\chapter{Limitation}
\input{chapters/Limitation.tex}
\chapter{Conclusion and Future Work}
\input{chapters/Conclusion.tex}


\bibliographystyle{apalike}
\bibliography{references}
\appendix
\chapter{Declaration of Consent}
\input{chapters/appendix.tex}

\end{document}

