


\textbf{Project: Glimpses of Palestine}


Declaration of consent for sound, image and video recordings



I,-------------------------------------- , have been informed orally by Samer Shawar that sound, image and video recordings of me will be made as part of the above project.

The recordings serve exclusively to view and analyze the evaluation again. They are recorded with a recording device and then potentially written down by the staff of the research project.

There is a chance I am recognizable in the footage. For this reason, all persons involve in the evaluation are subject to absolute confidentiality. The recordings will not be passed on to third parties.

I am aware that my statements in scientific papers are quoted in excerpts, and I was assured that they will be treated anonymously. Image extracts, on which I am shown, are anonymized before a possible publication. All information that could lead to the identification of my person will changed or removed from the text.

Since I can potentially be recognized in the recordings, I have the right to have these recordings deleted at any time without any disadvantages. To get recordings of me deleted, I contact the researcher.

The declaration of consent for sound, image and video recordings is voluntary. I can revoke this declaration of consent at any time. In the event of rejection or withdrawal, I will not incur no costs or other disadvantages. However, participation in the study will then not be possible.

Personal contact data are stored separately from interview data and are inaccessible to third parties. After completion of the research project, I have been assured that my contact data will be automatically deleted, unless I expressly agree to further storage for the contact option for topic-related research projects. I can object to longer storage at any time.

Participation in the research in voluntary. I may at any time cancel an interview, refuse further participation and withdraw my consent to a recording and transcript without any disadvantage to me.

\vspace{5mm}
I agree to take part in an interview/several interviews, workshops, and focus groups as part of the research project mentioned above.


 $\Box$ Yes \hspace{15mm}
 $\Box$ No

\vspace{10mm}
I agree to be contacted for future related research projects. For this my contact details about the end of the research project remain stored.


 $\Box$ Yes \hspace{15mm}
 $\Box$ No


\vspace{10mm}
I have received a copy of this declaration of consent.


 $\Box$ Yes \hspace{15mm}
 $\Box$ No



\vspace{5mm}
For question or other concerns, I can contact the following: 


Samer Shawar


Kohlbettstrasse 15


D-570072 Siegen


samer.shawar@student.uni-siegen.de

\vspace{15mm}

--------------------------------------------------  \hspace{20mm}            ---------------------------------------------


Place, Date and Signature of Participant	\hspace{15mm}         	Name of Participant in Block letters
\vspace{10mm}

--------------------------------------------------  \hspace{20mm}            ---------------------------------------------


Place, Date and Signature of Researcher	\hspace{15mm}         	Name of Researcher in Block letters
