This chapter will address the limitations that I encountered during my research. There were technological constraints during the development of the application. And there were also restrictions on the ground, by collecting data and documentation. In the first section, I will talk about the technological boundaries and in the second section, I will display the restriction on the maps in Palestine. 
 

\section{Technology}

Developing the application with the large capacity of videos showed the limitations of my computer. The videos were rendered and prepared every night, but the consequences were to fill the hard drive with data. However, I saved all the videos on external hard drives and I made a daily backup for my laptop data.  At some point, my laptop stopped working, it didn't restart and not even load a safe mode. I tried all the possibilities but nothing worked. I started to restore the data from the backup drive. After retrieving all the data back, and replace the lost data. Unfortunately, the Android \acrfull{sdk} in Unity didn't function anymore. Therefore I couldn't install the new copy of the application on my smartphone. The copy would include Al-Ghabisiyya in \acrshort{vr} after building it, also a lot of other scenes from the country. Technology here limited me and time constraints as well because it was the last week for me in the field and I needed to let users test the Application. Luckily I had the previous copy of the application on my smartphone, and I showed the users the village on the laptop how did it look like. 
   

\section{Access to Maps}

The maps in Palestine are very unique, even with the new technologies that we have. Google maps, for instance, have a lack of information about the Palestinian areas at the West-bank. That also implies to those demolished villages there is no information related to them. The maps or even pictures for these villages are very complicated and very rare to find. As I mentioned in the Background chapter, the Israeli government blocked all this data from being published. This limited me to obtain more information and maps to reconstruct the other villages. The map of Al-Ghabissiya was taken by the British mandate from an ariel photo. If I had access to ariel photos or maps I would have constructed more villages in Virtual Reality. 